Computationally Efficient Simulation of Queues: The \proglang{R} Package \pkg{queuecomputer}

### 2020-07-18 paper.tex
Improve understanding of some sentences and remove rpy2 from requirements

In the case of a $M/M/K$ system equilibrium distributions for
performance measures can be derived analytically. These derivations are 
found in standard queueing theory textbooks \citep{lipsky2008queueing,
  thomopoulos2012fundamentals}. For instance, the limit probability of
$N$ customers in the system $\Prob(N)$ is
%
\begin{align}
\Prob(0) &= \left[\frac{ (K \rho)^K}{K! (1 - \rho)} + 1 + \sum_{i=1}^{K-1} \frac{(K \rho)^i}{i!}   \right]^{-1}, \nonumber \\
\Prob(N) &= \begin{cases} 
\Prob(0) \frac{(K \rho)^n }{N!} & \quad  N \leq K,\\
\Prob(0) \frac{(K \rho)^n }{K! K^{N-K}} & \text{otherwise} ,
\end{cases} \label{eq:pn}
\end{align}
%
where $\rho$, the resource utilization, is defined as
$\frac{\lambda}{K \mu}$. For an $M/M/K$ system this is equal to the
expected number of busy servers divided by the total number of servers
$\frac{\E(B)}{K}$ \citep[p.~451]{cassandras2009introduction}. The
expected number of customers in the system is
\citep{bhat2015introduction}
%
\begin{align}
\E(N) = K\rho + \frac{\rho (K\rho)^K P(0)}{K!(1-\rho)^2} \label{eq:en},
\end{align}
%
and the expected waiting time is
%
\begin{align}
\E(\mathbf{w}) = \frac{(K \rho)^K P(0)}{K! K \mu(1-\rho)^2} \label{eq:ew}.
\end{align}
%
If the parameters of $f_{\boldsymbol{\delta}}$ and $f_{\mathbf{s}}$ are uncertain,
then we must turn to predictive distributions for estimates of
performance measures, which are computed analytically for $M/M/K$
queues (Equations~\ref{eq:en} and~\ref{eq:ew}). Predictive
distributions of performance measures using Bayesian posterior
distributions are derived by \citet{armero1994bayesian,
  armero1999dealing}.

@@

In a tandem queueing network, customers traverse an ordered series of
queues before departing the system. Real examples of such systems
include airport terminals, internet services and manufacturing
systems. In a parallel network, customers are partitioned into
different queueing systems, with their own two vectors $\mathbf{a}$ and $\mathbf{s}$.
In a fork/join network a task (another term for customer) is split into
a number of subtasks which are to be completed by distinct parallel
servers. The task is only complete once all its associated subtasks arrive
at the join point. One example of this situation is that of arriving passengers
and their bags at an airport.

>>>>

In the case of a $M/M/K$ system, these performance measures have 
equilibrium distributions which can be derived analytically. These derivations are 
found in standard queueing theory textbooks \citep{lipsky2008queueing,thomopoulos2012fundamentals}. 
For instance, the limit probability of $N$ customers in the system $\Prob(N)$ is
%
\begin{align}
\Prob(0) &= \left[\frac{ (K \rho)^K}{K! (1 - \rho)} + 1 + \sum_{i=1}^{K-1} \frac{(K \rho)^i}{i!}   \right]^{-1}, \nonumber \\
\Prob(N) &= \begin{cases} 
\Prob(0) \frac{(K \rho)^n }{N!} & \quad  N \leq K,\\
\Prob(0) \frac{(K \rho)^n }{K! K^{N-K}} & \text{otherwise} ,
\end{cases} \label{eq:pn}
\end{align}
%
where $\rho$, the resource utilization, is defined as
$\frac{\lambda}{K \mu}$. For an $M/M/K$ system this is equal to the
expected number of busy servers divided by the total number of servers
$\frac{\E(B)}{K}$ \citep[p.~451]{cassandras2009introduction}. The
expected number of customers in the system is
\citep{bhat2015introduction}
%
\begin{align}
\E(N) = K\rho + \frac{\rho (K\rho)^K P(0)}{K!(1-\rho)^2} \label{eq:en},
\end{align}
%
and the expected waiting time is
%
\begin{align}
\E(\mathbf{w}) = \frac{(K \rho)^K P(0)}{K! K \mu(1-\rho)^2} \label{eq:ew}.
\end{align}
%
If the parameters of $f_{\boldsymbol{\delta}}$ and $f_{\mathbf{s}}$ are uncertain,
then we must turn to predictive distributions for estimates of
performance measures, which are computed analytically for $M/M/K$
queues (Equations~\ref{eq:en} and~\ref{eq:ew}). Predictive
distributions of performance measures using Bayesian posterior
distributions are derived by \citet{armero1994bayesian,
  armero1999dealing}.

@@

In a tandem queueing network, customers traverse an ordered series of
queues before departing the system. Real examples of such systems
include airport terminals, internet services and manufacturing
systems. In a parallel network, the set of customers is partitioned into
different queueing systems, with their own two vectors $\mathbf{a}$ and $\mathbf{s}$.
In a fork/join network each task (another term for customer) is split into
a number of subtasks which are to be completed by distinct parallel
servers. The task is only complete once all its associated subtasks arrive
at the join point. One example of this situation is that of arriving passengers
and their bags at an airport.
